\documentclass{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage[hidelinks]{hyperref}
\usepackage{ifthen}

\input{requirement_macros.tex}

\title{Toolbox Plane}
\author{Paul Nykiel}
\date{\today}

\begin{document}
\maketitle
\tableofcontents
\section{Introduction}


\section{Requirements}

\group{Product}{Prod}
\dd
    {1}{Take-Off}
    {
        The airplane shall be launched by hand without an additional pilot. 
    }
    {
        This enables the launch by a single person, e.g. by throwing
        with automated acceleration and stabilization.
    }

\dd
    {2}{Climbing}
    {
        The airplane shall climb to a predefined altitude after launch and
        circle the launch site at this altitude. 
    }
    {
        Climbing and loitering guarantee a controlled environment
        for pre-mission checks.
    }

\dd
    {3}{Mission}
    {
        The airplane shall be able to follow a predefined set of waypoints, consisting
        of latitude, longitude and altitude. 
    }
    {
        This enables the implementation of a wide range of use-cases.
    }

\dd
    {4}{Landing}
    {
        The airplane shall be able to follow land at a predefined landing position.    
    }
    {
        A safe landing guarantees the fast reuse of the craft and the collection
        of all mission data.
    }
\dd
    {5}{Range}
    {
        The airplane minimum range of the aircraft shall be 100km
    }
    {
        This range allows for the execution of a wide range of missions.
    }
\dd
    {6}{Error Handling}
    {
        The airplane shall provide all information required for finding
        errors, both on the ground and when loitering.
    }
    {
        This allows for the fast detection of errors.
    }



\group{System High-Level}{Sys-HL}
\req
    {1}{Launch detection}
    {
        The system shall be able to detect launches via integrated sensors.
    }
    {
        \parent{Prod-DD-1}
    }
    {}
\req
    {2}{Velocity estimation}
    {
        The system shall be able to estimate the current velocity.   
    }
    {
        \parent{Prod-DD-1}, \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {3}{Velocity control}
    {
        The system shall be able to control the velocity depending on
        the current flight situation.
    }
    {
        \parent{Prod-DD-1}, \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {4}{Attitude estimation}
    {
        The system shall be able to estimate the current attitude.   
    }
    {
        \parent{Prod-DD-1}, \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {5}{Attitude control}
    {
        The system shall be able to control the attitude depending on
        the current flight situation.
    }
    {
        \parent{Prod-DD-1}, \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {6}{Position estimation}
    {
        The system shall be able to estimate the current position.
    }
    {
        \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {6}{Position control}
    {
        The system shall be able to fly to given positions.
    }
    {
        \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {7}{Mission Definition}
    {
        A mission, consisting of a list of waypoints with altitude
        and a target point shall be 
    }{}{}


\end{document}