\group{System High-Level}{Sys-HL}
\req
    {1}{Launch detection}
    {
        The system shall be able to detect launches if the
        acceleration is larger than \SI{6}{\meter \per \second^2}.
    }
    {
        \parent{Prod-DD-1}
    }
    {}
\req
    {2}{Velocity estimation}
    {
        The system shall be able to estimate the current velocity.   
        TODO precision.
    }
    {
        \parent{Prod-DD-1}, \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {3}{Velocity control}
    {
        The system shall be able to control the velocity
        TODO performance.
    }
    {
        \parent{Prod-DD-1}, \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {4}{Attitude estimation}
    {
        The system shall be able to estimate the current attitude.   
    }
    {
        \parent{Prod-DD-1}, \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {5}{Attitude control}
    {
        The system shall be able to control the attitude depending on
        the current flight situation.
    }
    {
        \parent{Prod-DD-1}, \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {6}{Position estimation}
    {
        The system shall be able to estimate the current position.
    }
    {
        \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {7}{Position control}
    {
        The system shall be able to fly to given positions.
    }
    {
        \parent{Prod-DD-2}, \parent{Prod-DD-3}, \parent{Prod-DD-4}
    }
    {}
\req
    {8}{Mission Definition}
    {
        A mission, consisting of a list of waypoints with altitude
        and a target point shall be able to be defined in a format
        readable by the plane.
    }
    {\parent{Prod-DD-3}, \parent{Prod-DD-4}}
    {}
\req
    {9}{Energy Storage}
    {
        The airplane has sufficient energy to complete the required distance
        of 100km.
    }
    {\parent{Prod-DD-5}}
    {}
\req
    {10}{Failure Tolerance}
    {
        The airplane can complete the required distance of 100km without
        failure of any mission-critical component. 
    }
    {\parent{Prod-DD-5}}
    {}
\req
    {11}{Debug Channel}
    {
        The airplane can transmit data while loitering
        at the launch site.
    }
    {\parent{Prod-DD-6}}
    {}
\req
    {12}{Debug Display}
    {
        Debug information transmitted by the plane can be displayed
        to the user.
    }
    {\parent{Prod-DD-6}}
    {}
\dd
    {1}{Partitioning}
    {
        The system is partitioned into the following components:
        \begin{itemize}
            \item Mechanical:
                \begin{itemize}
                    \item Airframe (AF)
                    \item Control Surfaces Actuators (CS) 
                    \item Electric Powertrain (PW)
                \end{itemize}
            \item Electronical:
                \begin{itemize}
                    \item Flightcontroller (FC)
                    \item Flightcomputer (FCP)
                    \item Power Distribution Board (PDB)
                    \item Navigation Board (NAV)
                    \item RC-Receiver (RX)
                    \item RC-Transmitter (TX)
                \end{itemize}
            \item Software:
                \begin{itemize}
                    \item Flightcontroller-Software (FCS)
                    \item Flightcomputer-Software (FCPS)
                    \item Power Distribution Board Software (PDBS)
                    \item Navigation Board Software (NAVS)
                \end{itemize}
        \end{itemize}
    }
    {
        This partitioning allows to implement the components
        individually from each other and thus allows to limit the complexity
        of the mission-critical components.
    }
\dd
    {2}{Manual override}
    {
        The system shall be able to be controlled manually
        while closer than 200m to the pilot.
    }
    {
        This allows handling errors during launch without
        risk of crashing.
    }

% TODO architecture